---
title: "First 19 Participants"
output:
  github_document:
    toc: true
---
Peek at data to check range of scores and main effect of song condition. Checking range out of concerns regarding variance for alexithymia moderation 

```{r setup, include=TRUE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readbulk)
library(psych)
library(afex)
library(knitr)
library(emmeans)
devtools::install_github("crsh/papaja")
library(sjPlot)
library(irr)
library(tableone)
devtools::install_github("ropenscilabs/gendercodeR")
library(gendercodeR)
library(interactions)
```

# Self Report Data 
```{r message = FALSE}
selfreport <- read_csv("First19Data/first19Qual.csv") 
selfreport <- genderRecode(input=selfreport,
                           genderColName = "gender", 
                           method = "narrow",
                           outputColName = "gender_recode", 
                           missingValuesObjectName = NA,
                           customDictionary = data.frame(stringsAsFactors=FALSE,
       Input = c("girl/female"),
      Output = c("female")))

selfreport <- selfreport %>% filter (id < 20)
print(nrow(selfreport))
```

## Describe demographics 
```{r}
selfreport %>% select(age, musichours) %>% describe() %>% kable(digits = 3)
selfreport <- selfreport %>% mutate(yearsplay = as.factor(yearsplay) %>% recode("6" = "5+"))
CreateTableOne(vars = c("gender_recode", "yearsplay"), data = selfreport) %>% kableone()
```

##Create scores 
###Alexithymia
```{r, message = FALSE, warning=FALSE}
selfreport <- selfreport %>% mutate(tas_4r = 6 - .$tas_4, #Reverse code items
                                    tas_5r = 6 - .$tas_5,
                                    tas_10r = 6 - .$tas_10,
                                    tas_18r = 6 - .$tas_18,
                                    tas_19r = 6 - .$tas_19)
EOTlist <- c("tas_5r", "tas_8", "tas_10r", "tas_15", "tas_16", "tas_18r", "tas_19r", "tas_20")
DDFlist <- c("tas_2", "tas_4r", "tas_11", "tas_12", "tas_17")
DIFlist <- c("tas_1", "tas_3", "tas_6", "tas_7", "tas_9", "tas_13", "tas_14")

tas <- selfreport %>% transmute(participant = .$id,
                                EOT = select(., EOTlist) %>% rowSums(),
                                DDF = select(., DDFlist) %>% rowSums(),
                                DIF = select(.,DIFlist) %>% rowSums(),
                                TAS = select(., EOT, DDF, DIF) %>% rowSums())

alpha(select(selfreport, EOTlist))$total$std.alpha
alpha(select(selfreport, DDFlist))$total$std.alpha
alpha(select(selfreport, DIFlist))$total$std.alpha

```

###DASS

```{r}
# S (Stress) Q1, 6, 8, 11, 12, 14, 18
# A (Anxiety) Q2, 4, 7, 9, 15, 19, 20
# D (Depression) Q3, 5, 10, 13, 16, 17, 21 

stresslist <- c("DASS_1", "DASS_6", "DASS_8", "DASS_11", "DASS_12", "DASS_14", "DASS_18")
anxietylist <- c("DASS_2", "DASS_4", "DASS_7", "DASS_9", "DASS_15", "DASS_19", "DASS_20")
depressionlist <- c("DASS_3", "DASS_5", "DASS_10", "DASS_13", "DASS_16", "DASS_17", "DASS_21")

dass <- selfreport %>% transmute(participant = .$id,
                                 stress = select(selfreport, stresslist) %>% rowSums(),
                            anxiety = select(selfreport,anxietylist) %>% rowSums(),
                            depression = select(selfreport,depressionlist) %>% rowSums())

alpha(select(selfreport, stresslist))$total$std.alpha
alpha(select(selfreport, anxietylist))$total$std.alpha
alpha(select(selfreport, depressionlist))$total$std.alpha
```

##Join scores
```{r}
scores <- full_join(dass, tas, by = "participant")
scores %>% select(-participant) %>% describe() %>% kable(digits = 2)
```



#Data Wrangle 
##Load in Data
```{r message = FALSE, warning = FALSE}
raw <- readbulk::read_bulk(directory = "First19Data", fun = read_csv)

raw <- unite(raw, 
             trialunique,
             participant, songmark, songtrials.thisRepN,
             remove = FALSE)

raw <- raw %>% mutate(.,
                      affectcat = as.factor(recode(affectcat,
                                                   "1" = "High Arousal/Positive Valence",
                                                   "2" = "High Arousal/Negative Valence",
                                                   "3" = "Low Arousal/Negative Valence",
                                                   "4" = "Low Arousal/Positve Valence")),
                      arousal = as.factor(recode(arousal, 
                                                 "1" = "Low",
                                                 "2" = "high")),
                      valence = as.factor(recode(valence,
                                                 "1" = "Negative",
                                                 "2" = "Positive")),
                      participant = as.numeric(participant))

#remove practice trial
filtered <- raw %>% filter(!is.na(song) & !(is.na(Instruction)))

filtered <- filtered %>% select(participant,
                                trialunique,
                                Word,
                                songmark,
                                valence,
                                arousal,
                                affectcat,
                                arousalkey.keys,
                                valencekey.keys,
                                likekey.keys,
                                WordResponse.keys) 


```

#Data Wrangling Emotion words 
```{r}
forspread <- filtered %>% filter (WordResponse.keys > 0) %>% select(trialunique,
                                                                    Word,
                                                                    WordResponse.keys)


spread <- forspread %>% spread(key = Word, value = WordResponse.keys)

```

## Affect ratings
```{r}
affectrating <- filtered %>% filter(!is.na(arousalkey.keys)) %>% select(trialunique,
                                                              participant,
                                                              songmark,
                                                              affectcat, 
                                                              valence,
                                                              arousal,
                                                              valencekey.keys,
                                                              arousalkey.keys)
```

##Merge affect and emotion ratings
```{r}
joinedaffectemo <- full_join(affectrating, spread, 
                    by = "trialunique") 
```

##Merge with questioniarre responses 
```{r}
joined <- full_join(joinedaffectemo, scores,
                    by = "participant")
```

# Emotion Differentiation 
## Create list of words
```{r}
poslist <- c("ACTIVE", "ALERT", "EXCITED", "HAPPY", "TENDER") #CHECK ALERT
neglist <- c("ANGRY", "ANXIOUS", "ASHAMED", "FRUSTRATED", "GUILTY", "SAD", "SCARED")
```

# Cretae negative and postive song data sets and participant list 
```{r}
negstim <- joinedaffectemo %>% filter(valence == "Negative")
posstim <- joinedaffectemo %>% filter(valence == "Positive")

participant <- (unique(joinedaffectemo$participant)) 

```

## Negative Stimuli
```{r}
icc_list_negstim=NULL
for(i in participant){
  participant_select <- filter(negstim, participant == i)
  stim_select <- select(participant_select, neglist)
  icc <- irr::icc(stim_select, model = "twoway", unit = "average")
  icc_temp <- icc$value
  fz_iccTemp <- fisherz(icc_temp)
  row_temp <- c(i, icc_temp, fz_iccTemp)
  icc_list_negstim=rbind(icc_list_negstim,row_temp)
  print(icc_temp)
} 

colnames(icc_list_negstim)=c("participant","ICCneg","ICCneg_fz")
icc_list_negstim=as.data.frame(icc_list_negstim)

```

## Positive Stimuli
```{r}
icc_list_posstim=NULL
for(i in participant){
  participant_select <- filter(posstim, participant == i)
  stim_select <- select(participant_select, neglist)
  icc <- irr::icc(stim_select, model = "twoway", unit = "average")
  icc_temp <- icc$value
  fz_iccTemp <- fisherz(icc_temp)
  row_temp <- c(i, icc_temp, fz_iccTemp)
  icc_list_posstim=rbind(icc_list_posstim,row_temp)
  print(icc_temp)
} 

colnames(icc_list_posstim)=c("participant","ICCpos","ICCpos_fz")
icc_list_posstim=as.data.frame(icc_list_posstim)
```

#Join ICC, make values inverse and mark negative (negative scores cannot be interpreted)
```{r}
joinedICC <- full_join(icc_list_posstim, icc_list_negstim, by = "participant")  %>% full_join(scores, by = "participant")

joinedICC <- joinedICC %>% mutate (ICCneg_keep = if_else(condition = joinedICC$ICCneg > 0,
                                                          true = "Positive",
                                                          false = "Ignore",
                                                          missing = "Ignore"),
                                    ICCpos_keep = if_else(condition = joinedICC$ICCpos > 0,
                                                          true = "Positive",
                                                          false = "Ignore",
                                                          missing = "Ignore"),
                                    ICCneg_r = 1 - joinedICC$ICCneg,
                                    ICCneg_fz_r = -1* joinedICC$ICCneg_fz,
                                    ICCpos_r = 1 - joinedICC$ICCpos,
                                    ICCpos_fz_r = -1* joinedICC$ICCpos_fz)  
```

# Describe and Plot Valence
```{r}
valencemodel <- afex::mixed(formula = valencekey.keys~affectcat*TAS + (1 |songmark) +(affectcat |participant), data = joined, return = "merMod") 
  
tab_model(valencemodel)

plot_model(valencemodel, type = "pred")$affectcat 

emmeans(valencemodel, "affectcat") %>% pairs() %>% kable(caption = "Pairwise comparisons of main effect of song affect category for valence ratings", digits = 3)

interact_plot(model = valencemodel,
              pred = TAS,
              modx = affectcat,
              x.label = "Alexithymia",
              y.label = "Rated Valence")
```

# Describe and Plot Arousal
```{r}
arousalmodel <- afex::mixed(formula = arousalkey.keys~affectcat*TAS + (1 |songmark) +(affectcat |participant), data = joined, return = "merMod") 
  
tab_model(arousalmodel)

plot_model(arousalmodel, type = "pred")$affectcat 

emmeans(arousalmodel, "affectcat") %>% pairs() %>% kable(caption = "Pairwise comparisons of main effect of song affect category for arousal ratings", digits = 3)

interact_plot(model = arousalmodel,
              pred = TAS,
              modx = affectcat,
              x.label = "Alexithymia",
              y.label = "Rated arousal")

```
