---
title: "Summarise"
output: github_document
---

```{r}
sum <- filtered %>% 
  group_by(participant, affectcat) %>%
  summarise(arousal = mean(arousalkey.keys),
            valence = mean(valencekey.keys),
            liking = mean(likekey.keys),
            TAS = mean(TAS))
```
# Self Report Data 
## Valence Self Report 
```{r valence model}
valencemodelsum <- lmer(valence~affectcat*TAS + (1 | participant), data = sum) 
tab_model(valencemodelsum)

anova(valencemodelsum)

sjPlot::plot_model(model = valencemodelsum,
                   type = "int",
                   mdrt.values = "meansd",
                   title = "Mean Self Report Valence",
                   grparticipant = FALSE) + 
  ggplot2::ylim(1, 5) + 
  ggplot2::geom_hline(yintercept = 3, linetype = "dotted") + 
  xlab("Affective Category") +
  ylab ("Rated Valence") + 
  theme_classic()

interactions::interact_plot(valencemodelsum,
                            pred = TAS,
                            modx = affectcat, 
                            interval = TRUE)  + 
  ylab("Rated Valence") + 
  xlab("TAS") + 
  ylim(1,5) +
  theme_classic()
```
## Liking
### Valence
```{r valence model}
valencemodellikingsum <- lmer(valence~affectcat*liking + (1 | participant), data = sum) 
tab_model(valencemodel)

interactions::sim_slopes(valencemodelliking,
                                pred = likekey.keys,
                                modx = affectcat)

sjPlot::plot_model(model = valencemodelliking,
                   type = "int",
                   mdrt.values = "meansd",
                   title = "Mean Self Report Valence",
                   legend.title = "Liking Rating",
                   grparticipant = FALSE) + 
  ggplot2::ylim(1, 5) + 
  ggplot2::geom_hline(yintercept = 3, linetype = "dotted") + 
  xlab("Affective Category") +
  ylab ("Rated Valence") + 
  theme_classic()


interactions::interact_plot(valencemodelliking,
                            pred = likekey.keys,
                            modx = affectcat,
                            interval = TRUE)  + 
  ylab("Rated Valence") + 
  xlab("Song Liking") + 
  theme_classic()
```



```{r}
tascor <- lmer(liking~affectcat*TAS + (1 | participant), data = sum)

tab_model(tascor)

sjPlot::plot_model(model = tascor,
                   type = "int")

interactions::interact_plot(model = tascor,
                            pred = TAS,
                            modx = affectcat)

interactions::probe_interaction(model = tascor,
                                pred = TAS,
                                modx = affectcat)

```


## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
