\documentclass[]{article}
    \usepackage{lmodern}
    \usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
  \else % if luatex or xelatex
\ifxetex
\usepackage{mathspec}
\usepackage{xltxtra,xunicode}
\else
  \usepackage{fontspec}
\fi
\defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
\newcommand{\euro}{€}
        \fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
  \usepackage{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
  \usepackage[right=1in,top=1.25in,bottom=1.25in,left=2.5in]{geometry}
  \ifxetex
\usepackage[setpagesize=false, % page size defined by xetex
            unicode=false, % unicode breaks when used with xetex
            xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
bookmarks=true,
pdfauthor={},
pdftitle={My social psychology preregistration based on van 't Veer and Giner-Sorolla (2016) template},
colorlinks=true,
citecolor=blue,
urlcolor=blue,
linkcolor=magenta,
pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% Customization for cos_prereg
\usepackage{longtable,booktabs,threeparttable,tabularx}
\linespread{1.5}
\newcounter{question}
\setcounter{question}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
\posttitle{
\begin{center}\large#1\end{center}
}
}

\setlength{\droptitle}{-2em}
\title{My social psychology preregistration based on van 't Veer and
Giner-Sorolla (2016) template}
\pretitle{\begin{changemargin}{-8pc}{0pc} \centering\large Preregistration\\ \Huge}
\posttitle{\end{changemargin}}
  \author{
          First Author\textsuperscript{1},
          Ernst-August Doelle\textsuperscript{1,2}          \\ \vspace{0.5cm}
              \textsuperscript{1} Wilhelm-Wundt-University\\
              \textsuperscript{2} Konstanz Business School      }

  \def\affdep{{"", ""}}%
  \def\affcity{{"", ""}}%
  \preauthor{\begin{changemargin}{-8pc}{0pc} \centering\large}
  \postauthor{\end{changemargin}}
\date{02. May 2019}
\predate{\begin{changemargin}{-8pc}{0pc} \centering\large\emph}
\postdate{\end{changemargin}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\lhead{}
\rhead{\large\textsc{\MakeLowercase{My preregistration}}}



% Title settings
\usepackage{titlesec}
\titleformat{\section}[display]{\bfseries\Large}{\thesection}{}{}[]
\titlespacing{\section}{0pc}{*3}{*1.5}
\titleformat{\subsection}[leftmargin]{\titlerule\bfseries\filleft}{\thesubsection}{.5em}{}
\titlespacing{\subsection}{8pc}{5ex plus .1ex minus .2ex}{1.5pc}
  

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi


\begin{document}
\maketitle
\vspace{2pc}


\newcommand\Question[2]{%
   \leavevmode\par
   \stepcounter{question}
   \noindent
   \textbf{\thequestion. #1}. #2\par}

\newcommand\Answer[1]{%
    \noindent
    \textit{Registered response}: #1\par}
    
\hypertarget{hypotheses}{%
\section{Hypotheses}\label{hypotheses}}

\hypertarget{predictions}{%
\subsection{Predictions}\label{predictions}}

Enter your response here.

\hypertarget{rationale-optional}{%
\subsection{Rationale (optional)}\label{rationale-optional}}

Enter your response here.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{design}{%
\subsection{Design}\label{design}}

Enter your response here.

\hypertarget{planned-sample}{%
\subsection{Planned sample}\label{planned-sample}}

Enter your response here.

\hypertarget{exclusion-criteria}{%
\subsection{Exclusion criteria}\label{exclusion-criteria}}

Enter your response here.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

Enter your response here.

\hypertarget{analysis-plan}{%
\section{Analysis plan}\label{analysis-plan}}

\hypertarget{confirmatory-analyses}{%
\subsection{Confirmatory analyses}\label{confirmatory-analyses}}

Enter your response here.

\hypertarget{details-of-analysis}{%
\subsection{Details of analysis}\label{details-of-analysis}}

Enter your response here.

\hypertarget{existing-data}{%
\subsection{Existing data}\label{existing-data}}

\textbf{Data collection has not begun.}

\textbf{Data collection is underway or complete but I have not yet
looked at the data.}

\textbf{Data collection is underway or complete and I have looked at the
data.}

\hypertarget{project-schedule-optional}{%
\subsection{Project schedule
(optional)}\label{project-schedule-optional}}

Enter your response here.

\hypertarget{further-comments-optional}{%
\subsection{Further comments
(optional)}\label{further-comments-optional}}

Enter your response here.

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{section}{%
\subsection{}\label{section}}

\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}

\noindent

\end{document}