---
title: "Data Analysis"
output: github_document
---

```{r setup, include=TRUE, message = FALSE}
library(tidyverse)
library(readbulk)
library(psych)
library(lme4)
library(knitr)
library(emmeans)
library(sjPlot)
library(irr)
#devtools::install_github("ropenscilabs/gendercodeR")
library(gendercodeR)
library(tableone)
library(visdat)
library(Hmisc)
library(naniar)
library(corrplot)
#devtools::install_github("ropensci/skimr") 
library(skimr)
```
# Self Report Data 
```{r check self report, message = FALSE}
survey <- read_csv(file = "SurveyData.csv")
vis_dat(survey) 
vis_miss(survey) 
```

## Recode gender
```{r recode gender, message = FALSE}
survey <- genderRecode(input=survey, 
                       genderColName = "gender", 
                       method = "narrow",
                       outputColName = "gender_recode", 
                       missingValuesObjectName = NA,
                       customDictionary = data.frame(stringsAsFactors=FALSE,
                                                     Input = c("girl/female"),
                                                     Output = c("female")))
```

## Describe demographics 
```{r describe demographics}
survey %>% select(age, musichours) %>% psych::describe() %>% kable(digits = 3)
survey <- survey %>% mutate(yearsplay = as.factor(yearsplay) %>% recode("6" = "5+"))
CreateTableOne(vars = c("gender_recode", "yearsplay"), data = survey) %>% kableone()
```

##Create scores 
###Alexithymia
```{r create TAS}
survey <- survey %>% mutate(tas_4r = 6 - .$tas_4, #Reverse code items
                            tas_5r = 6 - .$tas_5,
                            tas_10r = 6 - .$tas_10,
                            tas_18r = 6 - .$tas_18,
                            tas_19r = 6 - .$tas_19)
EOTlist <- c("tas_5r", "tas_8", "tas_10r", "tas_15", "tas_16", "tas_18r", "tas_19r", "tas_20")
DDFlist <- c("tas_2", "tas_4r", "tas_11", "tas_12", "tas_17")
DIFlist <- c("tas_1", "tas_3", "tas_6", "tas_7", "tas_9", "tas_13", "tas_14")


tas <- survey %>% transmute(participant = survey$id,
                            EOT = select(survey, EOTlist) %>% rowSums() %>% as.numeric(),
                            DDF = select(survey, DDFlist) %>% rowSums() %>% as.numeric(),
                            DIF = select(survey,DIFlist) %>% rowSums() %>% as.numeric(),
                            TAS = select(survey, EOTlist, DDFlist, DIFlist) %>% rowSums() %>% as.numeric(),
                            TASc = as.numeric(scale(TAS, scale = FALSE)))

alpha(select(survey, EOTlist))$total$raw_alpha
alpha(select(survey, DDFlist))$total$raw_alpha
alpha(select(survey,DIFlist))$total$raw_alpha
alpha(select(survey,EOTlist, DDFlist, DIFlist))$total$raw_alpha 
```

###DASS
```{r create DASS}
# S (Stress) Q1, 6, 8, 11, 12, 14, 18
# A (Anxiety) Q2, 4, 7, 9, 15, 19, 20
# D (Depression) Q3, 5, 10, 13, 16, 17, 21 

stresslist <- c("DASS_1", "DASS_6", "DASS_8", "DASS_11", "DASS_12", "DASS_14", "DASS_18")
anxietylist <- c("DASS_2", "DASS_4", "DASS_7", "DASS_9", "DASS_15", "DASS_19", "DASS_20")
depressionlist <- c("DASS_3", "DASS_5", "DASS_10", "DASS_13", "DASS_16", "DASS_17", "DASS_21")

dass <- survey %>% transmute(participant = .$id,
                             stress = select(survey, stresslist) %>% rowSums() ,
                             anxiety = select(survey,anxietylist) %>% rowSums(),
                             depression = select(survey,depressionlist) %>% rowSums())


alpha(select(survey, depressionlist))$total$raw_alpha
```

##Join scores
```{r joined TAS and DASS}
scores <- full_join(dass, tas, by = "participant")
scores %>% select(-participant) %>% psych::describe() %>% kable(digits = 2)
```
#Data Wrangle 
##Load in Data
```{r load psychopy, message = FALSE, warning = FALSE}
raw <- readbulk::read_bulk(directory = "PsychoPyData", fun = read_csv)
raw %>% sample_n(100) %>% vis_dat()
```
## set up data
```{r set up psychopy data}

trials <- drop_na(raw, songmark) # remove practice trials. Song mark only given during experiment

trials <- trials %>% mutate(participant = as.numeric(participant),
                            trialnum = songtrials.thisRepN + 1) 

trials <- trials %>% unite(col = trialunique,
                           participant, songmark, trialnum,
                           remove = FALSE) # give each trial for each participant a unique ID

```
## Label facotrs
```{r label factors}
trials <- trials %>% mutate(affectcat = as.factor(recode(affectcat,
                                                         "1" = "High Arousal/Positive Valence",
                                                         "2" = "High Arousal/Negative Valence",
                                                         "3" = "Low Arousal/Negative Valence",
                                                         "4" = "Low Arousal/Positve Valence")),
                            arousal = as.factor(recode(arousal, 
                                                       "1" = "Low",
                                                       "2" = "high")),
                            valence = as.factor(recode(valence,
                                                       "1" = "Negative",
                                                       "2" = "Positive")),
                            participant = as.numeric(participant))
```

# Data wrangle emotion words
```{r wrangle words}
wordresponse <- trials %>% filter (WordResponse.keys > 0) %>% select(trialunique,
                                                                    Word,
                                                                    WordResponse.keys)


wordspread <- wordresponse %>% spread(key = Word, value = WordResponse.keys)
vis_dat(wordspread)
print(nrow(wordspread)/max(trials$participant)) # get mean trials per participant
```

## Affect ratings
```{r affect ratings}
affectrating <- trials %>% filter(!is.na(arousalkey.keys)) %>% select(trialunique,
                                                              participant,
                                                              songmark,
                                                              affectcat, 
                                                              valence,
                                                              arousal,
                                                              valencekey.keys,
                                                              arousalkey.keys)

vis_dat(affectrating)
```

##Merge affect and emotion ratings
```{r merge words and affect ratings}
joinedaffectemo <- full_join(affectrating, wordspread, 
                             by = "trialunique")
vis_dat(joinedaffectemo) 
```

##Merge with questioniarre responses 
```{r merge psychopy with survey}
joined <- full_join(joinedaffectemo, scores,
                    by = "participant")

joined <- mutate(joined,
                 id = as.factor(participant),
                 songmark = as.factor(songmark))
vis_dat(joined)
```

# Describe data 
```{r describe data}

joined %>% select(TAS, TASc, depression) %>% skimr::skim() %>% skimr::kable() #Describe TAS and depression

joined %>% select(affectcat, songmark, arousalkey.keys, valencekey.keys) %>% group_by(affectcat) %>% skimr::skim(-affectcat, -songmark) %>% skimr::kable() # describe self report song ratings

select(joined, affectcat, arousalkey.keys, valencekey.keys, TAS, songmark) %>%  psych::describeBy(group = c("affectcat")) 
```
# Emotion Differentiation 
## Create list of words
```{r emotion word list}
poslist <- c("ACTIVE", "ALERT", "EXCITED", "HAPPY", "TENDER") #CHECK ALERT
neglist <- c("ANGRY", "ANXIOUS", "ASHAMED", "FRUSTRATED", "GUILTY", "SAD", "SCARED")
```

# Create negative and postive song data sets and participant list 
```{r split by song valence}
negstim <- joinedaffectemo %>% filter(valence == "Negative")
posstim <- joinedaffectemo %>% filter(valence == "Positive")

participant <- (unique(joinedaffectemo$participant)) 
```

## Negative Stimuli
```{r negative songs emotion differentiation}
icc_list_negstim=NULL
for(i in participant){
  participant_select <- filter(negstim, participant == i)
  stim_select <- select(participant_select, neglist)
  icc <- irr::icc(stim_select, model = "twoway", unit = "average")
  icc_temp <- icc$value
  row_temp <- c(i, icc_temp)
  icc_list_negstim=rbind(icc_list_negstim,row_temp)
  print(icc_temp)
} 

colnames(icc_list_negstim)=c("participant","ICCneg")

icc_list_negstim=as_tibble(icc_list_negstim)%>% replace_with_na_all(condition = ~.x < 0) #make data frame and remove below 0, neg numbers cannot be interpreted 

```

## Positive Stimuli
```{r positive songs emotion differentiation}
icc_list_posstim=NULL
for(i in participant){
  participant_select <- filter(posstim, participant == i) #select participant for loop
  stim_select <- select(participant_select, poslist) #select scores for positive words
  icc <- irr::icc(stim_select, model = "twoway", unit = "average") # get ICC for words for participant
  icc_temp <- icc$value #extract ICC
  row_temp <- c(i, icc_temp) # create participant row
  icc_list_posstim=rbind(icc_list_posstim,row_temp) 
  print(icc_temp)
} 

colnames(icc_list_posstim) <- c("participant","ICCpos")
icc_list_posstim <-as_tibble(icc_list_posstim) %>% replace_with_na_all(condition = ~.x < 0) #make data frame and remove below 0, neg numbers cannot be interpreted 

```

#Join ICC, make values inverse 
```{r join emotion differentiation}
joinedICC <- full_join(icc_list_posstim, icc_list_negstim, by = "participant")  %>% full_join(scores, by = "participant")

joinedICC <- joinedICC %>%  mutate(ICCneg_r = 1 - .$ICCneg, # reverse, higher scores = higher differentiation
                                   ICCneg_fz_r = -1* (fisherz(ICCneg)), #fisher z tranformation and reverse so that higher score = higher differentiation
                                   ICCpos_r = 1 - .$ICCpos,# reverse, higher scores = higher differentiation
                                   ICCpos_fz_r = -1*(fisherz(ICCpos)))#fisher z tranformation and reverse so that higher score = higher differentiation

joinedICC %>% select(contains("ICC")) %>% skimr::skim() %>% skimr::kable()

```

# Emotion Differentiation Correlations
```{r Differentiation Correlations}

DiffCorVar <- select(joinedICC, ICCneg_r, ICCneg_fz_r, ICCpos_r, ICCpos_fz_r, TAS)
DiffCorMatrix <- cor(select(joinedICC, ICCneg_r, ICCneg_fz_r, ICCpos_r, ICCpos_fz_r, TAS)) #variables for correlation
p.mat <- cor.mtest(DiffCorVar)

DiffCorPlot <- corrplot(corr = cor(DiffCorVar, use = "complete.obs"),
                        method = c("ellipse"),
                        type = c("upper"),
                        sig.level = c(.001, .01, .05),
                        p.mat = cor.mtest(DiffCorVar)$p,
                        insig = c("label_sig"))

```


# Describe and Plot Valence Self Report
```{r Valence self report GLM}
valencemodel <- lmer(valencekey.keys~affectcat*TAS + (1 |id) +(1 |songmark), data = joined) 

tab_model(valencemodel)

plot_model(valencemodel, type = "pred")$affectcat 

emmeans(valencemodel, "affectcat") %>% pairs() %>% knitr::kable(caption = "Pairwise comparisons of main effect of song affect category for valence ratings", digits = 3)

interactions::interact_plot(model = valencemodel,
              pred = TAS,
              modx = affectcat,
              x.label = "Alexithymia",
              y.label = "Rated Valence")

sjPlot::plot_model(model = lmer(valencekey.keys~songmark*TAS + (1 |id) , data = joined) ,
                   type ="int",
                   mdrt.values = "meansd")
```

# Describe and Plot Arousal
```{r Arousal self report GLM}
arousalmodel <- lme4::lmer(formula = arousalkey.keys~affectcat*TAS + (1 |participant) +(1 |songmark), data = joined) 

tab_model(arousalmodel)

plot_model(arousalmodel, type = "pred")$affectcat 

emmeans(arousalmodel, "affectcat") %>% pairs() %>% knitr::kable(caption = "Pairwise comparisons of main effect of song affect category for arousal ratings", digits = 3)



interactions::interact_plot(model = arousalmodel,
              pred = TAS,
              modx = affectcat,
              x.label = "Alexithymia",
              y.label = "Rated arousal")

interactions::sim_slopes(model = arousalmodel,
                         pred = TAS,
                         modx = affectcat)

```

```{r}
joined %>% select(valencekey.keys, arousalkey.keys, songmark) %>% dplyr::group_by(songmark) %>% skimr::skim() %>% skimr::kable()
```

