---
title: "Affect Ratings"
author: "joellarwood"
date: "2019-11-13"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# Analysis of self-reported experienced affect

For all analyses the fixed effect of Postive Valence and Low Arousal (or tender emotion) was the referent category. 



```{r SelfReportLoadin, echo = TRUE, results = FALSE, message = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(tidyverse)
library("sjPlot")
library("lmerTest")
library("interactions")
library(here)
library(cowplot)
library(svglite)

selfreport <- read_csv(here::here("data", "PsychoPyProcessed.csv")) %>% 
  rename(ValenceRating = valencekey.keys, 
         ArousalRating = arousalkey.keys, 
         LikingRating = likekey.keys) %>% 
  mutate(affectcat = fct_relevel(affectcat, "Low Arousal/Positve Valence"), 
         id = factor(id), #id as factor
         songmark = factor(songmark))
```

## Valence Ratings {.tabset}
### Registered Hypothesis
**People high in alexithymia will judge their experience of valence as more neutral for negative but not positively valenced music.** 

From the table below we can see that there is a significant effect of alexithymia for songs that were positively valenced and negative in arousal. With higher ratings of alexithymia predicting more neutral ratings of experienced valence. This is not consistent with our predictions and can also be seen in the plot below

```{r ValenceSelfReportConfirmRaw}

ValenceSelfConfirmRaw <- lmer(ValenceRating ~ affectcat*TAS + (1 | id) + (1|affectcat:songmark), data =selfreport)
tab_model(ValenceSelfConfirmRaw, show.std = "std")
```

```{r TASmeanSD}
minusTAS <- mean(selfreport$TAS, na.rm = TRUE)-sd(selfreport$TAS, na.rm = TRUE)

plusTAS <- mean(selfreport$TAS, na.rm = TRUE)+sd(selfreport$TAS, na.rm = TRUE)

meanTAS <- mean(selfreport$TAS, na.rm = TRUE)

```

```{r emmeansValenceConfirmRaw}
emmeans::emm_options(lmerTest.limit = 4000, 
                     pbkrtest.limit = 4000) # allow df calculations



ValenceConfirmGridRaw <- emmeans::ref_grid(ValenceSelfConfirmRaw, 
                                        at = list(TAS = c(minusTAS, meanTAS, plusTAS), # have alexithymia values for +/-1 SD 
                                                  affectcat = c("Low Arousal/Positve Valence", 
                                                                "High Arousal/Negative Valence",
                                                                "High Arousal/Positive Valence",
                                                                "Low Arousal/Negative Valence"))) 

ValenceConfirmGridRaw

emmeans::emmip(ValenceConfirmGridRaw, 
               affectcat~TAS, 
               CIs = TRUE, 
               xlab = "Alexithymia Scores", 
               ylab = "Predicted Valence Rating") + 
  ggplot2::theme_classic() + 
  ggplot2::theme(legend.title = element_blank()) +
  ggplot2::scale_fill_viridis_c() +
  ggplot2::ylim(c(1,5)) +
  ggplot2::geom_hline(yintercept = 3, linetype = "dashed") +
  ggplot2::scale_x_discrete(labels = c("-1SD", "Mean", "+1 SD"))
```

<br>In the table of slopes below it is evidenct that alexithymia only related to ratings of experienced valence when the song is positively valenced and low in arousal. 
```{r valenceslopesConfirm}
ValenceConfirmSlopesRaw <- emmeans::emtrends(ValenceSelfConfirmRaw, 
                  specs = "affectcat",
                  var = "TAS") # calculates trend of alexithymia at each level of affectcat

knitr::kable(ValenceConfirmSlopesRaw, format = "html", digits = 3) %>% kableExtra::kable_styling()
```

<br>The contrast of the slopes shows that the slopes for all other fixed effects are not differnt to each otehr (but are all different to the slope for postively valenced songs that are low in arousal. 

```{r VBalenecConfirmSlopePairwise}
knitr::kable(pairs(ValenceConfirmSlopesRaw)) %>% kableExtra::kable_styling()
``` 

### Exploratory tests

The model presented as confrimatory did not include potential covairates of liking of a song and of depression scores. Here I build models that add the liking by afectcat and depression by affectcat terms. The comparion of the models shows that the best fitting model includes the term for the liking of each song. 
```{r ValenceSelfExploreBuild}

ValenceSelfPlusLiking <- lmer(ValenceRating ~ affectcat*TAS + affectcat*LikingRating + (1 | id) + (1|affectcat:songmark), data =drop_na(selfreport))

ValenceSelfPlusDep <- lmer(ValenceRating ~ affectcat*TAS + affectcat*depression + (1 | id) + (1|affectcat:songmark), data =drop_na(selfreport))

ValenceSelfPlusLikingPLusDep <- lmer(ValenceRating ~ affectcat*TAS + affectcat*LikingRating + affectcat*depression + (1 | id) + (1|affectcat:songmark), data =drop_na(selfreport))

knitr::kable(anova(ValenceSelfPlusDep, ValenceSelfPlusLiking, ValenceSelfPlusLikingPLusDep), format = "html")
```

<br>The model that included liking also fit the data better than the hypothesised model 

```{r ValenceSelfExploreRegCompare}

SubsetValenceReg <- lmer(ValenceRating ~ affectcat*TAS + (1 | id) + (1|affectcat:songmark), data =drop_na(selfreport))
knitr::kable(anova(SubsetValenceReg, 
      ValenceSelfPlusLiking), format = "html", digits = 3)
```

<br>Here both models can be seen side by side. The second model is the model that included how much each song was liked. This model indicated that alexithymia predicted reduced experienced valence when the song was positive and low in arousal. However, this slope was only significantly different to the slopes for negatively valenced songs. 

```{r ValenceModelSideBySide}
sjPlot::tab_model(SubsetValenceReg, 
                  ValenceSelfPlusLiking,
                  show.std = "std")
```

<br>Despite the interaction, alexithymia only related to ratings of experienced valence when the song is positively valenced and low in arousal.
```{r ValenceModelExploreSlopes}
ValenceExploreSlopes <- emmeans::emtrends(ValenceSelfPlusLiking, var = "TAS", specs = "affectcat")

summary(ValenceExploreSlopes)
```
<br>The pairwise comparison of slopes adds more fidelity to the interaction. They indicate that the slopes for positvley valenced songs did not differ from eachother but that both postively valenced songs that were high in arousal and positively valenced songs that were low in arousal were significantly different to the slopes of the songs that were negatively valenced. 

```{r valenceExplorePairs}
knitr::kable(pairs(ValenceExploreSlopes), type = "html", digits = 3)
```


## Affect Ratings {.tabset}
### Registerd Hypothesis

**People high in alexithymia will have judge thier experience of arousal as more neutral when the music is positively valenced but not when it is negatively valenced**

From the table below it can be seen that alexithymia did not relate to self-reports of experienced arousal for songs that were positively valenced and low in arousal. It is also seen that the slopes of the other song catergries did not differ from the slope for positively valenced and low arousal songs. The slopes can also be seen in the plot below.]
```{r ArousalSelfReportConfirmRaw}

ArousalSelfConfirmRaw <- lmer(ArousalRating ~ affectcat*TAS + (1 | id) + (1|affectcat:songmark), data =selfreport)
tab_model(ArousalSelfConfirmRaw, show.std = "std")
```

```{r emmeansArousalConfirmRaw}
emmeans::emm_options(lmerTest.limit = 4000, 
                     pbkrtest.limit = 4000) # allow df calculations

ArousalConfirmGridRaw <- emmeans::ref_grid(ArousalSelfConfirmRaw, 
                                        at = list(TAS = c(minusTAS, meanTAS, plusTAS), # have alexithymia values for +/-1 SD 
                                                  affectcat = c("Low Arousal/Positve Valence", 
                                                                "High Arousal/Negative Valence",
                                                                "High Arousal/Positive Valence",
                                                                "Low Arousal/Negative Valence"))) 
emmeans::emmip(ArousalConfirmGridRaw, 
               affectcat~TAS, 
               CIs = TRUE, 
               xlab = "Alexithymia Scores", 
               ylab = "Predicted Arousal Rating"
               ) + 
  ggplot2::theme_classic() + 
  ggplot2::theme(legend.title = element_blank()) +
  ggplot2::scale_fill_viridis_c() +
  ggplot2::ylim(c(1,5)) + 
  ggplot2::geom_hline(yintercept = 3, linetype = "dashed") +
  ggplot2::scale_x_discrete(labels = c("-1SD", "Mean", "+1 SD"))
```
<br>The table of slopes also indicates that alexithymia did not relate to experiences of arousal for any of the songs. 

```{r ArousalSlopesConfirm}
ArousalConfirmSlopesRaw <- emmeans::emtrends(ArousalSelfConfirmRaw, 
                  specs = "affectcat",
                  var = "TAS")
knitr::kable(ArousalConfirmSlopesRaw, format = "html", digits = 3)
```

<br> From the slopes we see that alexithymia is not relating to experienced arousal for any song type. Given this the pairwise comparions are of little importance but presented for interest (and show that the only difference in slopes was between negatively valenced songs)
```{r ArousalConfirmSLopePairwise}}
knitr::kable(pairs(ArousalConfirmSlopesRaw), format = "html", digits = 3)
```

### Exploratory tests

The model presented as confrimatory did not include potential covairates of liking of a song and of depression scores. Here I build models that add the liking by afectcat and depression by affectcat terms when predicted experienced arousal
```{r ArousalSelfExploreBuild}

ArousalSelfPlusLiking <- lmer(ArousalRating ~ affectcat*TAS + affectcat*LikingRating + (1 | id) + (1|affectcat:songmark), data =drop_na(selfreport))

ArousalSelfPlusDep <- lmer(ArousalRating ~ affectcat*TAS + affectcat*depression + (1 | id) + (1|affectcat:songmark), data =drop_na(selfreport))

ArousalSelfPlusLikingPLusDep <- lmer(ArousalRating ~ affectcat*TAS + affectcat*LikingRating + affectcat*depression + (1 | id) + (1|affectcat:songmark), data =drop_na(selfreport))

knitr::kable(anova(ArousalSelfPlusDep, ArousalSelfPlusLiking, ArousalSelfPlusLikingPLusDep), 
             format = "html", 
             digits = 3)
```

<br> The comparison of models indicates that the best model is the one that includes the liking of the song covariate. Data for liking is not available for all participants but below I compare the models with and without liking.  

As can be seen blow the model with liking is preferred

```{r ArousalSelfExploreRegCompare}

SubsetArousalReg <- lmer(ArousalRating ~ affectcat*TAS + (1 | id) + (1|affectcat:songmark), data =drop_na(selfreport))
knitr::kable(anova(SubsetArousalReg, 
      ArousalSelfPlusLiking), format = "html", digits = 3)
```

<br>Here both models can be seen side by side. In the model that includes liking an interaction is present. The model terms indicate no effect of alexithymia on ratings of arousal for songs that were positively valenced and low in arousal. However, the slopes for songs that were high in arousal were significantly differnent to the slope when song were positively valenced and low in arousal 

```{r ArousalModelSideBySide}
sjPlot::tab_model(SubsetArousalReg, 
                  ArousalSelfPlusLiking, show.std = "std")
```

<br>The slopes indicate that increased alexithymia predicted reduced self-reported experience of arousal when the arousal of the song was high. There was no relationship between alexithymia and low arousal songs
```{r ArousalModelExploreSlopes}
ArousalExploreSlopes <- emmeans::emtrends(ArousalSelfPlusLiking, var = "TAS", specs = "affectcat")
knitr::kable(summary(ArousalExploreSlopes), format = "html", digits = 3)
```

<br>Finally, the pairwise comparions of slopes indicates that the slopes for high arousal songs were equivalent to each other and steeper than the slopes for all low arousal comparions. 
```{r exploreArousalPairwise}
knitr::kable(pairs(ArousalExploreSlopes), format = "html", digits = 3)
```

# Plot Exploratory models side by side 
```{r ModelPlot}
ValenceExploreGridRaw <- emmeans::ref_grid(ValenceSelfPlusLiking, 
                                        at = list(TAS = c(minusTAS, meanTAS, plusTAS), # have alexithymia values for +/-1 SD 
                                                  affectcat = c("Low Arousal/Positve Valence", 
                                                                "High Arousal/Negative Valence",
                                                                "High Arousal/Positive Valence",
                                                                "Low Arousal/Negative Valence"))) 

valenceplot <- emmeans::emmip(ValenceExploreGridRaw, 
                          affectcat~TAS, 
                          CIs = TRUE, 
                          xlab = "Alexithymia Scores", 
                          ylab = "Predicted Valence Rating"
) + 
  ggplot2::theme_classic() + 
  ggplot2::theme(legend.title = element_blank())+
  ggplot2::scale_fill_viridis_c() +
  ggplot2::ylim(c(1,5)) + 
  ggplot2::geom_hline(yintercept = 3, linetype = "dashed") +
  ggplot2::scale_x_discrete(labels = c("-1SD", "Mean", "+1 SD")) + 
    ggplot2::theme_classic() + 
  ggplot2::theme(legend.title = element_blank()) +
  ggplot2::scale_fill_viridis_c() +
  ggplot2::ylim(c(1,5)) + 
  ggplot2::geom_hline(yintercept = 3, linetype = "dashed") +
  ggplot2::scale_x_discrete(labels = c("-1SD", "Mean", "+1 SD")) +
  ggplot2::theme(text = element_text(family = "Times New Roman", 
                                     size = 12)) 

  

ArousalExploreGridRaw <- emmeans::ref_grid(ArousalSelfPlusLiking, 
                                        at = list(TAS = c(minusTAS, meanTAS, plusTAS), # have alexithymia values for +/-1 SD 
                                                  affectcat = c("Low Arousal/Positve Valence", 
                                                                "High Arousal/Negative Valence",
                                                                "High Arousal/Positive Valence",
                                                                "Low Arousal/Negative Valence"))) 
arousalplot <- emmeans::emmip(ArousalExploreGridRaw, 
                          affectcat~TAS, 
                          CIs = TRUE, 
                          xlab = "Alexithymia Scores", 
                          ylab = "Predicted Arousal Rating"
) + 
  ggplot2::theme_classic() + 
  ggplot2::theme(legend.title = element_blank()) +
  ggplot2::scale_fill_viridis_c() +
  ggplot2::ylim(c(1,5)) + 
  ggplot2::geom_hline(yintercept = 3, linetype = "dashed") +
  ggplot2::scale_x_discrete(labels = c("-1SD", "Mean", "+1 SD"))+
  ggplot2::theme(text = element_text(family = "Times New Roman", 
                                     size = 12)) 



legend <- get_legend(
  valenceplot + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

sideplot <- plot_grid(
  valenceplot + theme(legend.position = "none"), 
  arousalplot + theme(legend.position = "none"),
  align = 'vh',
  nrow = 1
)

sideplotlegend <- plot_grid(sideplot, legend, ncol = 1, rel_heights = c(1, .1))

ggsave(here::here("docs", "ValenceArousal.svg"))


```

