---
title: "Data Cleaning"
author: "joellarwood"
date: "2019-11-11"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---

Here the data import, processing, and cleaning steps taken can be followed and visualised 

```{r loadin, echo = FALSE, results = FALSE, message = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(tidyverse)
library(gendercodeR)
library(skimr)
library(readbulk)
library(visdat)
library(psych)
```

```{r importsurvey, results = FALSE}
survey <- read_csv(file = here::here("data", "RawSurvey.csv"))
```

```{r factorecode, results = FALSE}

survey <- survey %>% 
  mutate(gender_recoded = recode_gender(gender = gender, 
                                         fill = TRUE) %>% as_factor(), 
         yearsplay = as_factor(yearsplay) %>% recode("6" = "5+"),
         )

levels(survey$gender_recoded)
levels(survey$yearsplay)

survey <- survey %>% 
  mutate(gender_recoded = fct_recode(gender_recoded, 
                                     female = "Girl/Female"))
levels(survey$gender_recoded)
```

# Create scores 
## Alexithymia
```{r create TAS, echo = FALSE}
survey <- survey %>% 
  mutate(tas_4r = 6 - .$tas_4, #Reverse code items
         tas_5r = 6 - .$tas_5,
         tas_10r = 6 - .$tas_10,
         tas_18r = 6 - .$tas_18,
         tas_19r = 6 - .$tas_19)

EOTlist <- c("tas_5r", "tas_8", "tas_10r", "tas_15", "tas_16", "tas_18r", "tas_19r", "tas_20")
DDFlist <- c("tas_2", "tas_4r", "tas_11", "tas_12", "tas_17")
DIFlist <- c("tas_1", "tas_3", "tas_6", "tas_7", "tas_9", "tas_13", "tas_14")


survey <- survey %>% mutate(EOT = select(survey, EOTlist) %>% rowSums() %>% as.numeric(),
                            DDF = select(survey, DDFlist) %>% rowSums() %>% as.numeric(),
                            DIF = select(survey,DIFlist) %>% rowSums() %>% as.numeric(),
                            TAS = select(survey, EOTlist, DDFlist, DIFlist) %>% rowSums() %>% as.numeric(),
                            TASc = as.numeric(scale(TAS, scale = FALSE)))
# EOT alpha
eotalpha <- psych::alpha(select(survey, EOTlist))$total$raw_alpha

# DDF alpha
ddfalpha <- psych::alpha(select(survey, DDFlist))$total$raw_alpha

#DIF alpha
difalpha <- psych::alpha(select(survey,DIFlist))$total$raw_alpha

# TAS total alpha
tasalpha <- psych::alpha(select(survey,EOTlist, DDFlist, DIFlist))$total$raw_alpha
```
The internal consistency for total alerxithymia scores was `r tasalpha`

The internal consistency for DDF was `r ddfalpha`  
The internal consistency for DIF was `r difalpha`  
The internal consistency for EOT was `r eotalpha`

## Depression

```{r create DASS, results = FALSE}
# S (Stress) Q1, 6, 8, 11, 12, 14, 18
# A (Anxiety) Q2, 4, 7, 9, 15, 19, 20
# D (Depression) Q3, 5, 10, 13, 16, 17, 21 

#stresslist <- c("DASS_1", "DASS_6", "DASS_8", "DASS_11", "DASS_12", "DASS_14", "DASS_18")
#anxietylist <- c("DASS_2", "DASS_4", "DASS_7", "DASS_9", "DASS_15", "DASS_19", "DASS_20")
depressionlist <- c("DASS_3", "DASS_5", "DASS_10", "DASS_13", "DASS_16", "DASS_17", "DASS_21")

survey <- survey %>% 
  mutate(depression = select(survey, depressionlist) %>% rowSums()
                            )


depalpha <- psych::alpha(select(survey, depressionlist))$total$raw_alpha

```
The internal consistency for depression was `r depalpha`  

# PsychoPy Data 

```{r load psychopy, message = FALSE, warning = FALSE}
raw <- readbulk::read_bulk(directory = here::here("data", "PsychoPyData"), fun = read_csv)
```

# Identify Practice Trails and create trial ID
```{r new variable creation}
raw <- raw %>% 
  mutate(prac = if_else(is.na(.$songmark), "practice", "trial"),
         id = as.numeric(participant),
         trialnum = songtrials.thisRepN + 1,
         affectcat = as.factor(recode(affectcat,
                                      "1" = "High Arousal/Positive Valence",
                                      "2" = "High Arousal/Negative Valence",
                                      "3" = "Low Arousal/Negative Valence",
                                      "4" = "Low Arousal/Positve Valence")),
         targetemotion = as.factor(recode(affectcat, 
                                          "High Arousal/Positive Valence" = "Happy",
                                          "High Arousal/Negative Valence" = "Fear",
                                          "Low Arousal/Negative Valence" = "Sad",
                                          "Low Arousal/Positve Valence" = "Tender")),
         arousal = as.factor(recode(arousal, 
                                    "1" = "Low",
                                    "2" = "high")),
         valence = as.factor(recode(valence,
                                    "1" = "Negative",
                                    "2" = "Positive"))) %>% 
  unite(col = trialunique,
        id, songmark, trialnum,
        remove = FALSE)
```

## Clean word data 
### Ratings 
```{r clean word data}
emotionwords <- raw %>% 
  filter (WordResponse.keys > 0 & prac == "trial") %>% #emotion responses from trials
  select(trialunique,
         Word,
         WordResponse.keys) %>% 
  spread(key = Word, value = WordResponse.keys) # spread so each trial is only 1 column

vis_dat(emotionwords)
```
### Reaction times
```{r wordRT}
emotionwordsRT <- raw %>% 
  filter (WordResponse.keys > 0 & prac == "trial") %>% #emotion responses from trials
  select(trialunique,
         Word,
         WordResponse.rt) %>% 
  spread(key = Word, value = WordResponse.rt)
vis_dat(emotionwordsRT)
```
### Joined
```{r joinRTandRating}
emotionwords <- left_join(emotionwords, 
                          emotionwordsRT, 
                          by = "trialunique", 
                          suffix = c("_rating", "_RT"))
vis_dat(emotionwords)
```

## Affect ratings
```{r affect ratings}
affectrating <- raw %>% 
  filter(!is.na(arousalkey.keys) & prac == "trial") %>%
  select(trialunique,
         id,
         songmark,
         affectcat,
         targetemotion,
         valence,
         arousal,
         valencekey.keys,
         valencekey.rt,
         arousalkey.keys,
         valencekey.rt,
         likekey.keys,
         likekey.rt,
         prac)

vis_dat(affectrating)
```

## Putting datasets together
```{r merge words and affect ratings}
joinedaffectemo <- full_join(emotionwords, affectrating, 
                             by = "trialunique")


scores <- survey %>% select(id, 
                            depression, 
                            EOT, 
                            DDF, 
                            DIF, 
                            TAS, 
                            gender_recoded, 
                            musichours, 
                            yearsplay)

joined <- full_join(joinedaffectemo, scores,
                    by = "id") 

vis_dat(joined)

write_csv(joined, path = here::here("data", "PsychoPyProcessed.csv"))
write_csv(survey, path = here::here("data", "ProcessedSurvey.csv" ))
```

# Describe data 

```{r}
descriptives_joined <- joined %>% 
  filter(!is.na(id)) %>% 
  group_by(id) %>% 
  summarise(trialscompleted = n(), 
            DDF = mean(DDF), 
            EOT = mean(EOT), 
            DIF = mean(DIF), 
            TAS = mean(TAS), 
            DEP = mean(depression), 
            ) 

descriptives_survey <- scores %>% 
  filter(!is.na(id)) %>% 
  group_by(id) %>% 
  summarise(trialscompleted = n(), 
            DDF = mean(DDF), 
            EOT = mean(EOT), 
            DIF = mean(DIF), 
            TAS = mean(TAS), 
            DEP = mean(depression), 
            ) 
descriptives_both <- full_join(descriptives_joined, descriptives_survey, by = "id") 

descriptives_both <- descriptives_both %>% 
  mutate(EQdep = if_else(identical(DEP.x, DEP.y), 
                         "equal", "not"), 
         EQtas = if_else(identical(TAS.x, TAS.y), 
                         "equal", "not"), 
         EQeot = if_else(identical(EOT.x, EOT.y), 
                         "equal", "not"), 
         EQddf = if_else(identical(DDF.x, DDF.y), 
                         "equal", "not"), 
         EQdif = if_else(identical(DIF.x, DIF.y), 
                         "equal", "not")) 

tableone::CreateTableOne(data = select(descriptives_both, 
                                       -contains("y"),
                                       -contains("id"),
                                       contains("EQ"))) %>% 
  tableone::kableone(caption = "Descriptives of survey results. EQ variables indicate proportion of descriptive statistics that were identical across the survey dataset and the joined dataset indicating no errors in joining/manipulation")
```






