---
title: "Descriptives of Data"
author: "joellarwood"
date: "2019-11-14"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r echo = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(tidyverse)
library(corrr)
library(ggpubr)
library(tableone)
```

# Self Report Descriptives 

## Demographics and Questionairres 

```{r LoadDemographics, echo = FALSE}
demographics <- read_csv(here::here("data", "ProcessedSurvey.csv")) %>% 
  select(age, yearsplay, musichours, gender_recoded, TAS, EOT, DIF, DDF, depression) %>% 
  mutate(age = as_factor(age) %>% recode("18 years" = "18"), 
         gender = as_factor(gender_recoded), 
         yearsplay = as_factor(yearsplay) %>% fct_relevel("0", "1", "2", "3", "4", "5", "5+"), 
         age_num = as.numeric(as.character(age)))
```

### Age 
```{r Age}
tableone::CreateCatTable(vars = "age", data = demographics)

ggplot2::ggplot(demographics, aes(age)) + 
  geom_bar(fill = "light blue") + 
  theme_classic() 

ggpubr::ggdensity(data = demographics, 
                  x = "age_num", 
                  add = "mean", 
                  fill = "blue") 

```

The mean age was `r mean(demographics$age_num, na.rm = TRUE)` with a SD of `r sd(demographics$age_num, na.rm = TRUE)`

### Gender

```{r gender}

tableone::CreateCatTable(vars = "gender", data = demographics)

ggplot2::ggplot(demographics, aes(gender)) + 
  geom_bar(fill = "light blue") + 
  theme_classic()

```


### Years Played

```{r yearsplay}
tableone::CreateCatTable(vars = "yearsplay", data = demographics)

ggplot2::ggplot(demographics, aes(yearsplay)) + 
  geom_bar(fill = "light blue") + 
  theme_classic()
```

### Alexithymia and Depression

```{r selfreportmeasures}
demographics %>% select(TAS, DIF, DDF, EOT, depression) %>% skimr::skim()

##Critical correlaion is .18

demographics %>% 
  select(TAS, DIF, DDF, EOT, depression) %>% 
  drop_na() %>% 
  corrr::correlate() %>% 
  corrr::network_plot(min_cor = .18, 
                      colors = c("red","green", "blue"))
```

## Songs 
### Valence
```{r importpsychopy, echo = FALSE}

songdata <- read_csv(here::here("data", "PsychoPyProcessed.csv"))

```

### Arousal
```{r valenceplot}

affectdat <- songdata %>% 
  group_by(songmark) %>% 
  summarise(mean_Valence = mean(valencekey.keys), 
            sd_Valence = sd(valencekey.keys), 
            mean_Arousal = mean(arousalkey.keys), 
            sd_Arousal = sd(arousalkey.keys)) %>% 
  pivot_longer(-songmark, 
               names_to = c(".value", "Dimension"), 
               names_sep = "_", 
               values_drop_na = TRUE)

ggpubr::ggviolin(data = drop_na(songdata), 
                 x = "songmark",
                 xlab = "song",
                 y = "valencekey.keys", 
                 ylab = "valence rating",
                 fill = "valence",
                 ylim = c(1,5), 
                 add = "mean", 
                 caption = "Dot indicates mean")
```

```{r arousal}
ggpubr::ggviolin(data = drop_na(songdata), 
                 x = "songmark",
                 xlab = "song",
                 y = "arousalkey.keys", 
                 ylab = "arousal rating",
                 fill = "arousal",
                 ylim = c(1,5), 
                 add = "mean", 
                 caption = "Dot inidcates mean")
```

### Specific Emotions 

Each song and its target emotion are presented along with the mean ratings for that song. 

On visual observation it seems altert and maybe active are arousal rather valence discriminant

```{r specificemotions}
emotionratinglong <- songdata %>% 
  select(songmark, affectcat, contains("rating")) %>% 
  pivot_longer(cols = contains("rating"), 
             names_to = "emotion", 
             values_to = "rating"
             )

describeratings <- emotionratinglong %>% 
  group_by(songmark, emotion) %>% 
  summarise(Mean = round(mean(rating), digits = 2), 
            SD = round(sd(rating), digits = 2)) %>% 
  drop_na() %>% 
  mutate(target = if_else(songmark <= 4, 
                          "Fear", if_else(songmark == 5 | songmark == 6 | songmark == 7 | songmark == 8, 
                                          "Happy", if_else(songmark == 9 | songmark == 10 | songmark == 11 | songmark == 12,
                                                           "Sad", "Tender"))
                          ), 
         song = glue::glue("{target}_{songmark}")) 

ggplot2::ggplot(describeratings, 
                aes(x = emotion, 
                    y = Mean, 
                    fill = emotion
                )) +
  ggplot2::geom_errorbar(aes(ymin = Mean-SD, 
                             ymax = Mean + SD)) +
  facet_wrap("song") +
  geom_bar(stat = "identity") +
  theme_classic ()+
  theme(axis.text.x = element_text(size = 8, 
                                   angle = 270))

describeratings %>% 
  mutate(Mean_SD = glue::glue("{Mean} ({SD})")) %>% 
  select(song, emotion, Mean_SD) %>% 
  pivot_wider(names_from = emotion, 
              values_from = Mean_SD) %>% 
  knitr::kable()
```

