---
title: "Descriptives of Data"
author: "joellarwood"
date: "2019-11-14"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r message = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(tidyverse)
library(corrr)
library(ggpubr)
library(tableone)
library(corrr)
```

# Self Report Descriptives 

## Demographics and Questionairres 

```{r LoadDemographics, echo = FALSE}
demographics <- read_csv(here::here("data", "ProcessedSurvey.csv")) %>% 
  select(age, yearsplay, musichours, gender_recoded, TAS, EOT, DIF, DDF, depression) %>% 
  mutate(age = as_factor(age) %>% recode("18 years" = "18"), 
         gender = as_factor(gender_recoded), 
         yearsplay = as_factor(yearsplay) %>% fct_relevel("0", "1", "2", "3", "4", "5", "5+"), 
         age_num = as.numeric(as.character(age))) %>% 
  arrange(desc(age_num))
```

### Age 

The age of participants was heavily skewed to the 17-25 year old range
```{r Age}
tableone::CreateCatTable(vars = "age", data = demographics)

ggplot2::ggplot(demographics, aes(age_num)) +
  ggplot2::xlab("Age in years") +
  geom_bar(fill = "light blue") + 
  theme_classic() 

ggpubr::ggdensity(data = demographics, 
                  x = "age_num", 
                  add = "mean", 
                  fill = "blue") 

```

The mean age was `r mean(demographics$age_num, na.rm = TRUE)` with a SD of `r sd(demographics$age_num, na.rm = TRUE)`

### Gender

The participants were majority female. 
```{r gender}

tableone::CreateCatTable(vars = "gender", data = demographics)

ggplot2::ggplot(demographics, aes(gender)) + 
  geom_bar(fill = "light blue") + 
  theme_classic()

```


### Years Played

Generally speaking the participants had a high level of musical experience. 
```{r yearsplay}
tableone::CreateCatTable(vars = "yearsplay", data = demographics)

ggplot2::ggplot(demographics, aes(yearsplay)) + 
  geom_bar(fill = "light blue") + 
  theme_classic()
```

### Alexithymia and Depression

Alexithymia and depression related to eachother as is presented in the literature. Further half of the participants  fell into the normal range of scores for depression. 

```{r selfreportmeasures}
demographics %>% select(TAS, DIF, DDF, EOT, depression) %>% skimr::skim()

##Critical correlaion is .18

demographics %>% 
  select(TAS, DIF, DDF, EOT, depression) %>% 
  drop_na() %>% 
  corrr::correlate() %>% 
  corrr::network_plot(colors = c("red","green", "blue"))

demographics %>% 
  select(TAS, DIF, DDF, EOT, depression) %>% 
  apaTables::apa.cor.table()
```

## Songs 
### Valence

Negatively valence songs were generally rated as negative (i.e. below 3[Neutral]) while positively valenced songs tended to be rated more neutrally with the mean trending around 3
```{r importpsychopy, echo = FALSE}

songdata <- read_csv(here::here("data", "PsychoPyProcessed.csv"))

```

```{r valenceplot}

affectdat <- songdata %>% 
  group_by(songmark) %>% 
  summarise(mean_Valence = mean(valencekey.keys), 
            sd_Valence = sd(valencekey.keys), 
            mean_Arousal = mean(arousalkey.keys), 
            sd_Arousal = sd(arousalkey.keys)) %>% 
  pivot_longer(-songmark, 
               names_to = c(".value", "Dimension"), 
               names_sep = "_", 
               values_drop_na = TRUE)

ggpubr::ggviolin(data = drop_na(songdata), 
                 x = "songmark",
                 xlab = "song",
                 y = "valencekey.keys", 
                 ylab = "valence rating",
                 fill = "valence",
                 ylim = c(1,5), 
                 add = "mean", 
                 caption = "Dot indicates mean")
```
### Arousal
Arousal ratings were broadly distributed as expected, however the means were closer to neutral. 
```{r arousal}
ggpubr::ggviolin(data = drop_na(songdata), 
                 x = "songmark",
                 xlab = "song",
                 y = "arousalkey.keys", 
                 ylab = "arousal rating",
                 fill = "arousal",
                 ylim = c(1,5), 
                 add = "mean", 
                 caption = "Dot inidcates mean")
```


### Specific Emotions 

Each song and its target emotion are presented along with the mean ratings for that song. 

On visual observation it seems altert and maybe active are arousal rather valence discriminant. 

Generally speaking the target emotion (as specified by Vuoskoski and EErola, 2011) was among the hightest rated emotion for each song. 

```{r specificemotions}
emotionratinglong <- songdata %>% 
  select(songmark, affectcat, contains("rating")) %>% 
  pivot_longer(cols = contains("rating"), 
             names_to = "emotion", 
             values_to = "rating"
             )

describeratings <- emotionratinglong %>% 
  group_by(songmark, emotion) %>% 
  summarise(Mean = round(mean(rating), digits = 2), 
            SD = round(sd(rating), digits = 2)) %>% 
  drop_na() %>% 
  mutate(target = if_else(songmark <= 4, 
                          "Fear", if_else(songmark == 5 | songmark == 6 | songmark == 7 | songmark == 8, 
                                          "Happy", if_else(songmark == 9 | songmark == 10 | songmark == 11 | songmark == 12,
                                                           "Sad", "Tender"))
                          ), 
         song = glue::glue("{target}_{songmark}")) 

ggplot2::ggplot(describeratings, 
                aes(x = emotion, 
                    y = Mean, 
                    fill = emotion
                )) +
  ggplot2::geom_errorbar(aes(ymin = Mean-SD, 
                             ymax = Mean + SD)) +
  ggplot2::labs(title = "Mean emotion rating for each song", 
                caption = "Image can be opened full screen in a new window by") +
  facet_wrap("song") +
  geom_bar(stat = "identity") +
  theme_classic ()+
  theme(axis.text.x = element_text(size = 8, 
                                   angle = 270))

describeratings %>% 
  mutate(Mean_SD = glue::glue("{Mean} ({SD})")) %>% 
  select(song, emotion, Mean_SD) %>% 
  pivot_wider(names_from = emotion, 
              values_from = Mean_SD) %>% 
  knitr::kable(format = "html", digits = 3)
```

