---
title: "EmoDif"
author: "joellarwood"
date: "2020-01-06"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---
```{r PackageLoad, echo = TRUE, results = FALSE, message = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library("tidyverse")
library("sjPlot")
library("lmerTest")
library("here")
library("kableExtra")
library("icc")
library("naniar")
library(psych)
```

I need to split the data according to the valence of the stimulus presented and also create a vector of the postive and negative emotion terms
```{r loaddata}

ProcessedData <- read_csv(here::here("data", "PsychoPyProcessed.csv")) %>% 
  drop_na(songmark)


NegTrails <- ProcessedData %>% 
  filter(valence == "Negative")

PosTrials <- ProcessedData %>% 
  filter(valence == "Positive")


```

To get the emotion differentiation index I need to calculate the ICC for each participant

# Negative Emotion Differentiation
```{r NegDif}

participant <- unique(ProcessedData$id)

NegDif <- NULL # init empty data list for loop 

for (i in participant){
  p_select = filter(NegTrails, id == i)
  word_select = select(p_select, 
                       "ANGRY_rating", 
                       "ANXIOUS_rating", 
                       "ASHAMED_rating", 
                       "FRUSTRATED_rating", 
                       "GUILTY_rating",
                       "SAD_rating", 
                       "SCARED_rating")
  icc = irr::icc(word_select, model = "twoway", unit = "average")
  icc_temp = icc$value
  row_tmp = c(i, icc_temp)
  NegDif = rbind(NegDif, row_tmp)
  print(icc_temp)
}

colnames(NegDif) = c("id", "NegICC")

NegDif <- NegDif %>% 
  as_tibble() %>% 
  naniar::replace_with_na_at(
    .vars = c("NegICC"), 
    condition = ~(.x) < 0 # remove negative values as they cannot be interpreted 
  ) %>%  
  mutate(NegDif = 1 - NegICC,
         NegDif_fz = psych::fisherz(NegICC)
  )

```
The index from `r sum(is.na(NegDif$NegICC))` participants was not usable owing to being a negative ICC


# Positive Emotion Differentiation
```{r NegDif}


PosDif <- NULL # init empty data list for loop 

for (i in participant){
  p_select = filter(NegTrails, id == i)
  word_select = select(p_select, 
                       "ALERT_rating", 
                       "ACTIVE_rating", 
                       "EXCITED_rating", 
                       "HAPPY_rating", 
                       "TENDER_rating"
                       )
  icc = irr::icc(word_select, model = "twoway", unit = "average")
  icc_temp = icc$value
  row_tmp = c(i, icc_temp)
  PosDif = rbind(PosDif, row_tmp)
  print(icc_temp)
}

colnames(PosDif) = c("id", "PosICC")

PosDif <- PosDif %>% 
  as_tibble() %>% 
  naniar::replace_with_na_at(
    .vars = c("PosICC"), 
    condition = ~(.x) < 0 # remove negative values as they cannot be interpreted 
  ) %>%  
  mutate(PosDif = 1 - PosICC,
         PosDif_fz = psych::fisherz(PosICC)
  )

```
The index from `r sum(is.na(PosDif$PosICC))` participants was not usable owing to being a negative ICC


Now I want to merge the emotion differntiation data with the self report data 

```{r merge}

MergedDif <- ProcessedData %>% 
  select(id, depression:yearsplay) %>% 
  distinct(id, .keep_all = TRUE) %>% 
  inner_join(NegDif, by = "id") %>% 
  inner_join(PosDif, by = "id") 

```

Now I want to see the simple correaltions 
```{r}

MergedDif %>% 
  dplyr::select(TAS, DDF, DIF, EOT, depression, NegDif_fz, PosDif_fz) %>% 
  apaTables::apa.cor.table(filename = "docs/emotionDifCorrelations.rtf")


```
And I will also look at the distributions 
```{r}

```

I also want to do some exploratory regressions as well as my registered regression 

```{r}


PosDifReg <- lm(PosDif_fz~TAS, 
                data = MergedDif)
plot_qq(PosDifReg)
```

