---
title: "Specific Emotions"
author: "joellarwood"
date: "2019-11-20"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

The aim of this study was to look at ratings and physiology in terms of valence and arousal. However, we also have data on specific emotions and each excerpt used had a *a priori* target emotion. 

This gives us a long form of the data that has a colum `targetrating` which gives the self-reported rating for the songs target emotion. 
```{r PAckageLoad, echo = TRUE, results = FALSE, message = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(tidyverse)
library("sjPlot")
library("lmerTest")
library("interactions")
library(here)
```

```{r DataLoad}
SpecificEmotion <- read_csv(here::here("data", "PsychoPyProcessed.csv")) %>% 
  mutate(targetemotion = fct_relevel(targetemotion, "Tender"), 
         songmark = as_factor(songmark), 
         id = as_factor(id),
         targetrating = if_else(targetemotion == "Fear", 
                                SCARED_rating, 
                                if_else(targetemotion == "Sad", 
                                        SAD_rating, 
                                        if_else(targetemotion == "Tender", 
                                                TENDER_rating, 
                                                HAPPY_rating)))) %>% 
  rename(liking = likekey.keys)

SpecificEmotion %>% select(contains("target"), 
                           contains("rating")) %>% 
  head(15) %>% 
  knitr::kable()
```

The data still has a number of variables in it but many of these are not of consequence to the model. The variables of interest are `targetrating` (outcome) `targetemotion` (predictor), `TAS` (predictor) `liking` (covariate), `id` (grouping factor of participant) and `songmark` (random factor of the song listened to). 

Target emotion has been set as the referent level. 

The model fit is improved by including the liking variable but this does not change the interpretation of the results. However, the AIC indicates neither model is a good fit. The slope for alexithymia when the song is tender is significant and negative. However, all other slopes are different to it. 

```{r model}

SpecEmoModel <- lmer(targetrating ~ targetemotion*TAS + (1 | id) + (1|targetemotion:songmark), data =drop_na(SpecificEmotion, liking))

SpecEmoModelLiking <- lmer(targetrating ~ targetemotion*TAS + targetemotion*liking + (1 | id) + (1|targetemotion:songmark), data =drop_na(SpecificEmotion, liking))

knitr::kable(anova(SpecEmoModel, 
                   SpecEmoModelLiking), 
             digits = 3, 
             format = "html"
             )

tab_model(SpecEmoModel,
          SpecEmoModelLiking,
          show.std = "std", 
          show.r2 = TRUE,
          show.aic =  TRUE)
```

